---
title: "Homework_9"
author: "Sijay Matsinye"
date: "4/5/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1) Show and use a census API key that gives you access to the ACS data. Do not use my API key, use and show
your own key.
```{r }
#install.packages("tidycensus")
library(tidycensus)
library(tidyverse)
library(dplyr)
library(ggplot2)
```

2) Using ACS census data from 2015, show and use R code to do the following:
a) Produce a tibble that shows the median income estimates and the margin of errors for white males in the counties of California. The required variable code starts with the characters BO1OO1.Use the table to find the other characters.
The first five rows of your tibble are provided below:
```{r}
census_api_key("e1aaecf134a4cb5aa008d32d7c432fb38f041db4")
install = TRUE

v15 <- load_variables(2015, "acs5", cache = TRUE)

#View(v15)

CA <- get_acs(
  geography = "county",
  variables = c(medincome = "B01001A_011"),
  state = "CA",
  year = 2015
)

CA



mean(CA$moe)
median(CA$estimate)

```

b) Use a dplyr functions to change your table of part a so that it reflects estimates that are greater than $30,000 dollars and list the estimates in descending order.

```{r}
CA %>%
  filter(estimate > 30000) %>%
  arrange(desc(estimate)) -> CA_over_30

CA_over_30
```

c) Using the tibble that you produced in part b, use and show R code that will show the county that has a median income estimate of 51644 and a margin of error of 667.

```{r}
CA_over_30 %>%
  filter(estimate == 51644 & moe == 667)
```

d) Use and show ggplot coding that will produce the following boxplot for the data that you generated for part b.
```{r}
CA_over_30 %>%
  ggplot(aes(x = estimate)) +
  geom_boxplot(color = "black", fill = "red")
```

e) Use and show R code that will produce the following graph for the data generated in part b

```{r}
CA_over_30%>%
  mutate(NAME = gsub(" County, California", "", NAME)) %>%
  ggplot(aes(x = estimate, y = reorder(NAME, estimate))) +
  geom_errorbarh(aes(xmin = estimate - moe, xmax = estimate + moe)) +
  geom_point(color = "blue", size = 3) +
  labs(title = "Median Income for White Males by County",
       subtitle = "2014-2018 American Community Survey",
       y = "",
       x = "ACS estimate (bars represent margin of error)")


```